---
title: "Homework 1"
author: "Hannah Briggs"
output: github_document
---

Below are my solutions to HW 1.

```{r}
library(tidyverse)
```


## Problem 1

Create a data frame comprised with the specified elements.

```{r create_df}
prob1_df = 
  tibble(
    samp = rnorm(10),
    samp_gt_0 = samp > 0, 
    vec_char = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
    vec_factor = factor(c("low", "low", "low", "mod", "mod", "mod", "mod", "high", "high", "high"))
)

```

Take the mean of each variable in the data frame.

```{r mean_df}
mean(pull(prob1_df, samp))
mean(pull(prob1_df, samp_gt_0))
mean(pull(prob1_df, vec_char))
mean(pull(prob1_df, vec_factor))
```

We are able to take the mean of numbers and logical variables, but not character or factor variables.

Convert the logical, character, and factor variables (output not shown):

```{r convert_var, eval = FALSE}
as.numeric(pull(prob1_df, samp_gt_0))
as.numeric(pull(prob1_df, vec_char))
as.numeric(pull(prob1_df, vec_factor))
```

The logical variable can be converted to numeric as the output is assigned a binary value of 0 or 1, corresponding to yes or no (if sample value is greater than 0), and why our mean is less than 1.

Character variables cannot be converted to numeric, with an output of "NA", which is why we are unable to compute a mean for this variable.

Factor variables can be converted and assigned a number value to indicate their corresponding level.

Convert the logical vector:

```{r convert_multiply_df}
as.numeric(pull(prob1_df, samp_gt_0)) * pull(prob1_df, samp)
as.factor(pull(prob1_df, vec_char)) * pull(prob1_df, samp)
as.numeric(as.factor(pull(prob1_df, vec_factor)))* pull(prob1_df, samp)
```

## Problem 2