---
title: "Homework 1"
author: "Hannah Briggs"
output: github_document
---

Below are my solutions to HW 1.

```{r}
library(tidyverse)
```


## Problem 1

Create a data frame comprised with the specified elements.

```{r create_df}
prob1_df = 
  tibble(
    samp = rnorm(10),
    samp_gt_0 = samp > 0, 
    vec_char = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
    vec_factor = factor(c("low", "low", "low", "mod", "mod", "mod", "mod", "high", "high", "high"))
)

```

Take the mean of each variable in data frame.

```{r mean_df}
mean(pull(prob1_df, samp))
mean(pull(prob1_df, samp_gt_0))
mean(pull(prob1_df, vec_char))
mean(pull(prob1_df, vec_factor))
```

We are able to take the mean of numbers and logical variables, but not character or factor variables.

Convert the logical, character, and factor variables (output not shown):

```{r convert_var, eval = FALSE}
as.numeric(pull(prob1_df, samp_gt_0))
as.numeric(pull(prob1_df, vec_char))
as.numeric(pull(prob1_df, vec_factor))
```

What happens, and why? Does this help explain what happens when you try to take the mean?

Convert the logical, character, and factor variables, and multiply by random sample:

```{r convert_multiply_df}
as.numeric(pull(prob1_df, samp_gt_0)) * pull(prob1_df, samp)
as.numeric(pull(prob1_df, vec_char)) * pull(prob1_df, samp)
as.numeric(pull(prob1_df, vec_factor)) * pull(prob1_df, samp)
```

## Problem 2